%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvtwoposentries}

%---------------------------------------------------------
  \cvtwoposentry
    {Software Development Engineer} % Job title
    {December, 2016 - Present} % Date(s)
    {Associate Software Engineer}
    {June, 2015 - November, 2016}
    {Qualcomm India Private Limited} % Organization
    {Hyderabad, India} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designing and implementing Over-The-Air (OTA) upgrade solutions on Linux Android platform. This is how Android smartphones are upgraded to new software releases. \newline
        The focus is on designing fault-tolerant software - a bug in OTA software can brick your smartphone for good..}
        \item {Debugging Android Framework issues and upstreaming fixes to the \textbf{Android Open Source Project} (AOSP). I deal with race-conditions, memory-leaks, heap/stack corruptions on a daily basis.}
        \item {Developing/maintaining tools that facilitate debugging (of memory-leaks and heap-corruptions for the most part}
        \item {Bringing up Android userspace on new Qualcomm Snapdragon chipsets. This calls for extensive knowledge of filesystems(ext4/ubifs), bootup (kernel-to-init), IPC (binder), etc}
        \item {I also contribute to the \textbf{AOSP}, which is where the Android that runs on your smartphones comes from. This means that atleast a couple of bug-fixes authored by me make their way to millions of Android smartphones regardless of whether they use Qualcomm's Snapdragon chipsets or not. \newline
        To view/review my upstreamed AOSP commits, visit: \textit{\textbf{\url{https://android-review.googlesource.com/q/shibin}}}}
      \end{cvitems}
    }

%---------------------------------------------------------
  
%---------------------------------------------------------
\end{cvtwoposentries}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {May, 2014 - July, 2014} % Date(s)
    {Qualcomm India Private Limited} % Organization
    {Hyderabad, India} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {This was my first experience with the Android OS. I worked on an optimization designed for the Android composition engine (SurfaceFlinger) and built a basic prototype for the same. The project required detailed understanding of Android source code related to the composition engine. (A composition engine is responsible for acquiring windows/layers from various applications and then compositing the final image that gets displayed on your screen)}
      \end{cvitems}
    }
  
%---------------------------------------------------------
\end{cventries}

%\cventry{May, 2014 -
%July, 2014}
%{Interim Engineering Intern}
%{Android Performance}
%{\textsc{Qualcomm India Private Limited}}
%{Hyderabad}
%{Worked on optimization designed for the Android composition engine (SurfaceFlinger) and built a basic prototype for the same. The project required detailed understanding of Android source code related to the composition engine.}

